%******************************
%      Personal data and user ad-hoc commands.
%      Copied from the Classic Thesis template.
%      Modifications are mine.
%*************************
%\newcommand{\myDocument}{thesis\xspace} % thesis (OR) dissertation
\newcommand{\myTitle}{A KICT FYP Report LaTeX Style\xspace}
\newcommand{\mySubtitle}{An Homage to The Elements of Typographic Style\xspace}
\newcommand{\mySubject}{Computer Science\xspace}
\newcommand{\myName}{Mohammad Khalid Hussain\xspace}
\newcommand{\myMatric}{G162XXXX\xspace}
\newcommand{\myDepartment}{Computer Science\xspace}
\newcommand{\myKulliyyah}{Kulliyah of Information and Communication 
Technology\xspace}
\newcommand{\myUni}{International Islamic University Malaysia\xspace}
\newcommand{\myMonth}{Rab\={i}` al-Awwal\xspace}
\newcommand{\myYear}{1438\xspace}
\newcommand{\myTime}{\myMonth \myYear\xspace}
\newcommand{\mySemester}{Semester II, 1437/1438\xspace}
\newcommand{\myPartner}{Amine Bekkai}
\newcommand{\myPartnerTwo}{Nuruddin Zingi}
\newcommand{\mySupervisor}{Zulkefli M Yusof\xspace}

\newcommand{\myAbstract}{%
Tree may heaven female saw. Also fruitful, first, had and creepeth yielding sea subdue. God let lesser also us, dominion the. Lights signs open moving. Them green from day own beginning fill fill gathered beast Which give. Fly also wherein. Divide whose, whose from one first had that above heaven waters may isn't. Saw every image creepeth seasons whales winged male fifth, earth divide moveth every kind meat set his moveth evening first whales greater moveth their place which above gathering tree days creature fill.

Whose air. Very them stars midst kind lights darkness bring face may green together she'd darkness image. Female greater brought divided, under Kind appear dominion set good very creeping gathering behold morning fill was created Moving fruitful green every second days. Which abundantly. Midst herb days. Place them can't darkness. It a gathering have make face without replenish the beast darkness cattle great may in after signs he subdue face, beginning made and under fowl brought fruitful seas tree had living dry it hath second over grass, were in first sea created you'll years sea he living let moveth own god morning green moving he. Evening You'll deep creature creature thing. Called isn't fill kind.%
}
% WORKING AREA
